Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-10 WRITEUP/ms.tex
added comment on extraplanr flows

The high pressure observed in \flower (see \Fig{Mach_stellarRatio}, see also \citealt{Pallottini17a})
is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation?} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
high due to the resolution limit.
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy 
%\MM{This is a highly dissipative process.  Hennebelle \&
%  Klessen found it could only be important in rather small galaxies.
%  Does \flower qualify?} 
would also render the MCCs gravitationally unbound (see e.g., \citealt{Dobbs11a}), 
%\MM{Dobbs
%  started with a low-density disk, and got low-density clouds. I don't
%  think that's what you have here.  Do you have any evidence for
%  inter-cloud collisions being important?}
%\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
which would be consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.

>>>>

The high pressure observed in \flower (see \Fig{Mach_stellarRatio}, see also \citealt{Pallottini17a})
is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation? Clarify citations and
  mergers vs accretion...} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
high due to the resolution limit.
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy 
%\MM{This is a highly dissipative process.  Hennebelle \&
%  Klessen found it could only be important in rather small galaxies.
%  Does \flower qualify?} 
would also render the MCCs gravitationally unbound (see e.g., \citealt{Dobbs11a}), 
%\MM{Dobbs
%  started with a low-density disk, and got low-density clouds. I don't
%  think that's what you have here.  Do you have any evidence for
%  inter-cloud collisions being important?}
%\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
which would be consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
